Peridynamic Plates and Flat Shells: A non-ordinary, state-based model

### 2014-04-28 PlatePaper.tex
added h-convergence and minimum horizon plots

Additionally, the simply-supported flat plate is a configuration with significant analytical treatment, making a better comparison case than configurations that may require comparison to finite element or other solution techniques.
%
\subsection{Results}
The simplest test case for this model is a linear-elastic square plate with Poisson's ratio \(\nu = \sfrac{1}{3}\) that is simply-supported on all 4 sides with a uniform transverse pressure load on the entire surface between the supports.
As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:elastic_plate} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity.
Accurate results require a denser discretization than is the case for the elastic beams from previous work.

%
\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_n.pgf}}
  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection}
  \label{fig:elastic_plate}
\end{figure}

>>>>

Additionally, the simply-supported flat plate is a configuration with significant analytical treatment, making a better comparison case than configurations that may require comparison to finite element or other solution techniques.
%
\subsection{Results}
The simplest test case for this model is a linear-elastic square plate with Poisson's ratio \(\nu = \sfrac{1}{3}\) that is simply-supported on all 4 sides with a uniform transverse pressure load on the entire surface between the supports.
As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:plate_convergence_h} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity as the horizon length shrinks.
The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is sufficient.
The difference is evident in \cref{fig:plate_minimum_h}.

%
\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_h.pgf}}
  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Smaller Horizons}
  \label{fig:plate_convergence_h}
\end{figure}

%
\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_minimum_h.pgf}}
  \caption{Horizon Must Include Sufficient Nodes}
  \label{fig:plate_minimum_h}
\end{figure}

Accurate results require a denser discretization than is the case for the elastic beams from previous work.
\Cref{fig:plate_convergence_n} illustrates the model converging to the analytical solution as the discretization is made finer.

%
\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_n.pgf}}
  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Finer Dsicretization}
  \label{fig:plate_convergence_n}
\end{figure}
